Experiment 3: ratings

### 2021-06-07 analysis/exp3_analysis.Rmd
added data tables

```{r cars}
library(png)
library(grid)
library(ggplot2)
library(xtable)
require(here)
require(tidyverse)
require(tidyboot)
library(apa) # for generating APA-style text to report statistical tests
library(ggpubr)
require(gridExtra)
require(papaja)
require(kableExtra)
#require(qualtRics)
require(lmerTest)
require(ggpubr)
```

@@

int_agg <- int_long %>% mutate(rating = as.numeric(rating)) %>%
  group_by(drop, choice) %>%
  summarise(interest = mean(rating) - 1) 
# also want ratings scaled 0-1?
```

@@

```{r}
adult_agg <- adult_agg %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(target_likelihood = likelihood) %>%
  left_join(lik_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(distractor_likelihood = likelihood)

adult_agg <- adult_agg %>% left_join(int_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(target_interest = interest) %>%
  left_join(int_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(distractor_interest = interest)

adult_agg <- adult_agg %>% 
  mutate(prop_target_likelihood = target_likelihood / (target_likelihood + distractor_likelihood),
         prop_target_interest = target_interest / (target_interest + distractor_interest))
```

@@

```{r}
child_agg <- child_agg %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(target_likelihood = likelihood) %>%
  left_join(lik_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(distractor_likelihood = likelihood)

child_agg <- child_agg %>% left_join(int_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(target_interest = interest) %>%
  left_join(int_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(distractor_interest = interest)

child_agg <- child_agg %>% 
  mutate(prop_target_likelihood = target_likelihood / (target_likelihood + distractor_likelihood),
         prop_target_interest = target_interest / (target_interest + distractor_interest))
```

@@

```{r}
m_lik <- lm(chose_target ~ relation * prop_target_likelihood, data=adult_agg)
m_int <- lm(chose_target ~ relation * prop_target_interest, data=adult_agg)
summary(m_lik) # Rsq = .63
summary(m_int) # Rsq = .84
anova(m_lik, m_int)

m3 <- lm(chose_target ~ relation * prop_target_likelihood + relation * prop_target_interest, data=adult_agg)
summary(m3)
```

```{r}
p1 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

p2 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Interestingness") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

@@

```{r}
p1 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

p2 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Interestingness") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

@@

>>>>

```{r cars}
library(png)
library(grid)
library(ggplot2)
library(xtable)
require(here)
require(tidyverse)
require(tidyboot)
library(apa) # for generating APA-style text to report statistical tests
library(ggpubr)
require(gridExtra)
require(papaja)
require(kableExtra)
#require(qualtRics)
require(lmerTest)
require(ggpubr)
require(DT)
```

@@

int_agg <- int_long %>% mutate(rating = as.numeric(rating)) %>%
  group_by(drop, choice) %>%
  summarise(interest = mean(rating) - 1) 
# also want ratings scaled 0-1?

results_table <- lik_agg %>% left_join(int_agg) %>%
  arrange(desc(likelihood))

datatable(results_table) %>% formatRound(columns=c("likelihood","interest"), digits=3)
```

@@

```{r}
adult_agg <- adult_agg %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(targ_lik = likelihood) %>%
  left_join(lik_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(dist_lik = likelihood)

adult_agg <- adult_agg %>% left_join(int_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(targ_int = interest) %>%
  left_join(int_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(dist_int = interest)

adult_agg <- adult_agg %>% 
  mutate(prop_targ_lik = targ_lik / (targ_lik + dist_lik),
         prop_targ_int = targ_int / (targ_int + dist_int))
```

@@

```{r}
child_agg <- child_agg %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(targ_lik = likelihood) %>%
  left_join(lik_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(dist_lik = likelihood)

child_agg <- child_agg %>% left_join(int_agg, by=c("drop"="drop", "target"="choice")) %>%
  rename(targ_int = interest) %>%
  left_join(int_agg, by=c("drop"="drop", "distractor"="choice")) %>%
  rename(dist_int = interest)

child_agg <- child_agg %>% 
  mutate(prop_targ_lik = targ_lik / (targ_lik + dist_lik),
         prop_targ_int = targ_int / (targ_int + dist_int))
```

## Adult Choices vs. Ratings Table

```{r}
adult_agg %>% relocate(relation) %>% 
  relocate(distractor, .after=target) %>% 
  relocate(prop_targ_lik, .after=dist_lik) %>%
  DT::datatable() %>% 
  formatRound(columns=c("chose_target","targ_lik","dist_lik",
                        "targ_int","dist_int","prop_targ_lik",
                        "prop_targ_int"), digits=3)
```

@@

```{r}
m_lik <- lm(chose_target ~ relation * prop_targ_lik, data=adult_agg)
m_int <- lm(chose_target ~ relation * prop_targ_int, data=adult_agg)
summary(m_lik) # Rsq = .63
summary(m_int) # Rsq = .84
anova(m_lik, m_int)

m3 <- lm(chose_target ~ relation * prop_targ_lik + relation * prop_targ_int, data=adult_agg)
summary(m3)
```

```{r, fig.width=7.0, fig.height=3.8}
p1 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_targ_lik, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson") 
  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_targ_lik, 
               label = paste(..rr.label.., sep = "~`,`~")))

p2 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_targ_int, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Interestingness") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson")
  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_targ_int, 
               label = paste(..rr.label.., sep = "~`,`~")))

@@

```{r, fig.width=7.0, fig.height=3.8}
p1 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_targ_lik, color=relation)) + geom_point() +
  xlab("Proportion of Children Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson") 
  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_targ_lik, 
               label = paste(..rr.label.., sep = "~`,`~")))

p2 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_targ_int, color=relation)) + geom_point() +
  xlab("Proportion of Children Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Interestingness") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson")
  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_targ_int, 
               label = paste(..rr.label.., sep = "~`,`~")))

@@

## Compare Likelihood Ratings to Physics Models

```{r, fig.width=7.0, fig.height=3.8}
load(here("models/model_data.RData")) # mdat, all_trials_mse, all_trials_mse_r, etc.
# load(here("models/support_probability_fit_df.RData"))

# compare to support probability
supp_prob <- mdat %>% select(drop, target, relation, support_probability)

trials <- adult_agg %>% select(drop, target, distractor, relation) %>%
  left_join(supp_prob, by=c("drop","target","relation")) %>%
  rename(targ_supp_prob = support_probability) %>%
  left_join(supp_prob, by=c("drop"="drop", "distractor"="target", "relation"="relation")) %>%
  rename(dist_supp_prob = support_probability) %>%
  mutate(prop_target_supp = (targ_supp_prob) / (targ_supp_prob + dist_supp_prob + 1e-5))

p1 <- adult_agg %>% left_join(trials %>% select(drop, target, distractor, relation, prop_target_supp)) %>%
  ggplot(aes(x=prop_target_supp, y=prop_targ_lik, color=relation)) + geom_point(alpha=.8) +
  xlab("Proportion Target Support in Model") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson") 
  stat_cor(inherit.aes = F, aes(x=prop_target_supp, y=prop_targ_lik, 
               label = paste(..rr.label.., sep = "~`,`~")))

## compare to support sharpness
supp_tmp <- mdat %>% select(drop, target, relation, support_std)

trials <- adult_agg %>% select(drop, target, distractor, relation) %>%
  left_join(supp_tmp, by=c("drop","target","relation")) %>%
  rename(targ_supp_std = support_std) %>%
  left_join(supp_tmp, by=c("drop"="drop", "distractor"="target", "relation"="relation")) %>%
  rename(dist_supp_std = support_std) %>%
  mutate(prop_target_supp = (targ_supp_std) / (targ_supp_std + dist_supp_std + 1e-5))

p2 <- adult_agg %>% left_join(trials %>% select(drop, target, distractor, relation, prop_target_supp)) %>%
  ggplot(aes(x=prop_target_supp, y=prop_targ_lik, color=relation)) + geom_point(alpha=.8) +
  xlab("Prop. Target Support SD in Model") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson") 
  stat_cor(inherit.aes = F, aes(x=prop_target_supp, y=prop_targ_lik, 
               label = paste(..rr.label.., sep = "~`,`~")))
